Holomorphic field theories and higher algebra

### 2023-08-15 highervertexops.tex
describing anomaly in simple terms

\section{A model for punctured affine space}

@@

Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA_2$, $p \colon \sfA_2 \to \sfH_2$, given by the direct sum description of the corollary above.

\begin{rmk}
The inclusion $i$ is a map of commutative dg algebras.
Note that $p$ is not a map of algebras; for example
\beqn
p(z_1 \lambda_1) = \frac12
\eeqn
as $z_1 \lambda_1$ admits an orthogonal decomposition
\beqn
z_1 \lambda_1 = \frac12 (z_1 \lambda_1 - z_2 \lambda_2) + \frac12 .
\eeqn
\end{rmk}

Define the degree $-1$ operator 
\beqn
H \colon \sfA_2 \to \sfA_2 [-1]
\eeqn
by the condition that $H|_{\sfR_{0,b}\omega} = 0$ and 
\beqn
H(z_1^a \lambda_2^b) = \frac{1}{(b+1)} z_1^{a-1} \lambda_2^{b+1} .
\eeqn
Extend this to all of $\sfA_2$ using $SU(2)$ equivariance.
Note that for $a > 0$ this is an operator 
\beqn
H \colon \sfR_{a,b} \omega \to \sfR_{a-1,b+1} .
\eeqn

\begin{prop}
The triple $(p,i,H)$ defines a special deformation retract between $\sfA$ and its cohomology.
\end{prop}

\section{Distributions on punctured affine space}

@@

>>>>

\section{Models for functions and distributions on punctured affine space}

@@

Let $\sfH \define H^\bu(\sfA)$ and let $i,p$ be the $SU(2)$-equivariant inclusions and projections $i \colon \sfH_2 \hookrightarrow \sfA$, $p \colon \sfA \to \sfH$, given by the direct sum description of the corollary above.

There is a canonical contracting homotopy 
\beqn
H \colon \sfA \to \sfA[-1]
\eeqn 
because for each $b > 0$, there is a canonical equivariant inverse $\sfR_{a,b} \to \sfR_{a+1,b-1} \omega$.
Explicitly, send the highest weight vector $z_1^{a+1} \lambda_2^{b-1} \omega$ to the highest weight vector $z_1^{a} \lambda_2^{b}$ and then determine where other vector go via the lowering operator.
For $b = 0$, $H|_{\sfR_{0,b}\omega} = 0$.

\owen{Check the side conditions!}

\begin{lem}
The data $(i,p,H)$ determines a deformation retraction where $i$ is a map of dg commutative algebras.
\end{lem}

Note that $p$ is not a map of algebras. 
For example,
\beqn
p(z_1 \lambda_1) = \frac12
\eeqn
as $z_1 \lambda_1$ admits a decomposition
\beqn
z_1 \lambda_1 = \frac12 (z_1 \lambda_1 - z_2 \lambda_2) + \frac12 .
\eeqn

\subsection{Distributions on punctured affine space}

@@

\section{Recollection on anomalies for quantum moment maps}

Let $V$ be a dg vector space and let $V^* = \Hom(V, \CC)$ denote its dual complex. 
Consider the dg Poisson algebra $\cP = \Sym(V \oplus V^*)$ whose Poisson bracket extends the skew-symmetrized evaluation pairing on $V \oplus V^*$.
We view $\cP$ as functions on the cotangent bundle~$T^* V$.
Observe that the quadratic functions form a dg Lie subalgebra
\[
\cP_2 = (\Sym^2(V \oplus V^*), \{-,-\})
\]
of $\cP$.

There is a natural deformation quantization of $\cP$ as a Weyl algebra $\cW$.
Observe that there is a dg Lie subalgebra
\[
\cW_2 = (\Sym^2(V \oplus V^*) \oplus \Sym^0(V \oplus V^*), [-,-])
\]
of $\cW$.
It is a central extension of $\cP_2$, and let $\omega \in H^2(\cP_2)$ denote the associated 2-cocycle.

Suppose that there is a Lie algebra map $J: \fg \to \cP_2$.
We view as a special class of symmetries for the free theory encoded by $\cP$:
these are the symmetries where $\fg$ deforms the system to another {\em free} system.
This situation appears in the free field realization we are studying.

\begin{lem}
Given a Lie algebra map $J: \fg \to \cP_2$, the obstruction to lifting it to a map of Lie algebras $\fg \to \cW_2$ is the 2-cocycle $J^* \omega \in H^2(\fg)$.
\end{lem}

We call $J^*\omega$ the {\em anomaly} for quantizing this symmetry.

\begin{cor}
If the anomaly $J^*\omega$ does not vanish, then there is an $L_\infty$ algebra map $J^q: \widehat{\fg} \to \cW_2$ out of the $L_\infty$ extension
\[
\CC \to \widehat{\fg} \to \fg.
\]
\end{cor}
